Dark matter web in the Universe

### 2018-06-15 Draft/Chapter1/intro.tex
bruce

Large scale structures with  highly anisotropic shapes were first theoretically predicted by Zel'dovich approximation (hereafter ZA) \citep{Zeldovich1970}. The model based on ZA suggested that the eigenvalues of the deformation tensor dictate the shapes of the {\it collapsed} structures at the beginning non-linear stage of gravitational instability (\citealt{Arnold1982}, see also \citealt{Shandarin1989} and \citealt{Hidding2014}). These structures were found to be crudely  characterized as two-, one- and zero- dimensional  which actually meant that three characteristic scales of each structure ($L_1\ge L_2\ge L_3$) are approximately related as  $L_1^{(p)} \approx L_2^{(p)} \gg L_3^{(p)}$ or $L_1^{(f)} \gg L_2^{(f)} \approx L_3^{(f)}$ or $L_1^{(h)} \approx L_2^{(h)}  \approx L_3^{(h)} $ respectively.  In addition it implied that $L_1^{(p)} \approx L_1^{(f)}$ and $L_3^{(p)} \approx L_2^{(f)} \approx L_1^{(h)}$.\footnote{The multi-scale character of the cosmic web was not discussed until 1990s.} At present these generic types of structures are referred to as  walls/pancakes/sheets/membranes, filaments and haloes. Although the accuracy of the Zel'dovich approximation deteriorates from pancakes to  filaments and especially to halos on qualitative level  there are no more types of  structures. Altogether these structures contain the most of mass in the universe nevertheless they occupy  very little space. The most of space is almost empty  and is referred to as voids.

@@

Thus by the  early 1990s it was clearly demonstrated that the web like structure is a generic type for a wide range of initial conditions in both two-(\citealt{Melott1990}, \citealt{Beacom1991}) and three- dimensional \citep{Melott1993} cosmological N-body simulations. However it also was demonstrated that the quantitative parameters of the web structures depend on the initial power spectrum. Remarkably the simulations also showed that  adding small scale perturbations does not ruin the large scale structures if the slope of the power spectrum is negative in both two- and three- dimensional simulations.

@@

\section{Significance and Impact of the Cosmic Web}
% From Paper2018
Understanding the nature of the cosmic web is important for a variety of reasons. Quantitative measures of the cosmic web 
may provide information about the dynamics of gravitational structure formation, the background cosmological model, the 
nature of dark matter and ultimately the formation and evolution of galaxies. Since the cosmic web defines the fundamental spatial organization of matter and galaxies on scales of one to tens of Megaparsecs, its structure probes a wide variety of scales, form the linear to the nonlinear regime. This suggests that quantification of the cosmic web at these scales should provide a significant amount of 
information regarding the structure formation process. As yet, we are only at the beginning of systematically exploring the various 
structural aspects of the cosmic web and its components towards gaining deeper insights into the emergence of spatial 
complexity in the Universe \citep[see e.g.][]{Cautun2014a}.

@@

The mysterious dark matter that constitutes about 85\% of all mass in the Universe. Clustering of dark matter plays the dominant role in the formation of all observed structures on scales from a fraction to a few hundreds of Mega-parsecs. On these large scales, the dark matter distribution is broadly classified into voids, walls, filaments and haloes. Although this characterization is deeply enrooted in dynamical framework by Zel'dovich Approximation \cite{Zeldovich1970}, vast majority of the current classification schemes employ techniques based on static portrait of the web -- like the clustering information of dark matter particles (density thresholds, linking lengths etc.), structural features (eigenvalue analyses, connectivities etc.). In this thesis we demonstrate a novel approach to dynamical understanding of the cosmic web features -- fundamentally based on Zel'dovich Approximation, and it's direct consequence of multistreaming phenomenon.

However, it has to be noted and stressed that almost all the results here pertain to dark matter structures, not baryonic matter distribution of galaxies, stars or gas. While clustering of galaxies is positively correlated with dark matter concentrations, the difference in their dynamics is vast. Perhaps the most important difference in the context of this thesis is the difference of collisional cross-sections. Dark matter particles are collisionless in N-body simulations, hence display multiple velocity streams. The motion of cold gas resembles that of dark matter only until the first singularity arises. However, streams of gas cannot penetrate through one another, causing layers of neighboring gas layers to collide and result in shock waves. On galactic scales, the gas dynamics is further complicated by processes like radiative cooling and heating, supernova feedback, star formation and more.

@@

This thesis is a comprehensive collection of various cosmic structure analyses in the context of Lagrangian sub-manifold -- from topological studies of voids, to environmental investigation of dark matter haloes. In Chapter \ref{chapter2}, we give a brief overview of topics related to rest of the thesis -- including Zel'dovich Approximation. Lagrangian sub-manifold and multistream fields. Chapter \ref{chapter3} approaches to quantify thresholds based on multistreams with the cosmic web structures. The next two chapters deal with deeper understanding of topological and geometrical features detected in multistream field (in Chapter \ref{chapter4}) and a new approach of detecting dark matter haloes that is independent of heuristic parameters (in Chapter \ref{chapter5}). Comparison of a variety of current cosmic structure finding algorithms are compared with our multistream-based methodology in Chapter \ref{chapter3b}. The concluding Chapter \ref{chapter6} highlights future avenue of similar studies on the Lagrangian sub-manifold -- including detection of caustic surfaces and halo substructure analysis using flip-flop fields.

>>>>

Large scale structures with  highly anisotropic shapes were first theoretically predicted by the Zel'dovich approximation (\citealt{Zeldovich1970} and later elaborated in \citealt{Shandarin1989}, hereafter referred to as {\it the ZA}). The model based on the ZA suggested that the eigenvalues of the deformation tensor dictate the shapes of the {\it collapsed} structures at the beginning non-linear stage of gravitational instability (\citealt{Arnold1982}, see also \citealt{Shandarin1989} and \citealt{Hidding2014}). These structures were found to be crudely  characterized as two-, one- and zero- dimensional  which actually meant that three characteristic scales of each structure ($L_1\ge L_2\ge L_3$) are approximately related as  $L_1^{(p)} \approx L_2^{(p)} \gg L_3^{(p)}$ or $L_1^{(f)} \gg L_2^{(f)} \approx L_3^{(f)}$ or $L_1^{(h)} \approx L_2^{(h)}  \approx L_3^{(h)} $ respectively.  In addition it implied that $L_1^{(p)} \approx L_1^{(f)}$ and $L_3^{(p)} \approx L_2^{(f)} \approx L_1^{(h)}$.\footnote{The multi-scale character of the cosmic web was not discussed until 1990s.} At present these generic types of structures are referred to as pancakes/walls/sheets/membranes, filaments and haloes. Although the accuracy of the ZA deteriorates from pancakes to  filaments and especially to halos on qualitative level  there are no more types of  structures. Altogether these structures contain the most of mass in the universe nevertheless they occupy  very little space. The most of space is almost empty  and is referred to as voids.

@@

Thus by the  early 1990s it was clearly demonstrated that the web like structure is a generic type for a wide range of initial conditions in both two-(\citealt{Doroshkevich1989}, \citealt{Melott1990} and \citealt{Beacom1991}) and three- dimensional \citep{Melott1993} cosmological N-body simulations. However it also was demonstrated that the quantitative parameters of the web structures depend on the initial power spectrum. Remarkably the simulations also showed that  adding small scale perturbations does not ruin the large scale structures if the slope of the power spectrum is negative in both two- and three- dimensional simulations.

@@

\section{Significance and Impact of the Cosmic Web}
% From Paper2018
Understanding the nature of the cosmic web is important for a variety of reasons. Quantitative measures of the cosmic web 
may provide information about the dynamics of gravitational structure formation, the background cosmological model, the 
nature of dark matter (hereafter DM) and ultimately the formation and evolution of galaxies. Since the cosmic web defines the fundamental spatial organization of matter and galaxies on scales of one to tens of Megaparsecs, its structure probes a wide variety of scales, form the linear to the nonlinear regime. This suggests that quantification of the cosmic web at these scales should provide a significant amount of 
information regarding the structure formation process. As yet, we are only at the beginning of systematically exploring the various 
structural aspects of the cosmic web and its components towards gaining deeper insights into the emergence of spatial 
complexity in the Universe \citep[see e.g.][]{Cautun2014a}.

@@

The mysterious dark matter that constitutes about 85\% of all mass able to cluster in the Universe. Clustering of dark matter plays the dominant role in the formation of all observed structures on scales from a fraction to a few hundreds of Mega-parsecs. On these large scales, the dark matter distribution is broadly classified into voids, walls, filaments and haloes. Although this characterization is deeply enrooted in dynamical framework by the ZA \citep{Zeldovich1970, Shandarin1989}, vast majority of the current classification schemes employ techniques based on static portrait of the web -- like the clustering information of dark matter particles (density thresholds, linking lengths etc.), structural features (eigenvalue analyses, connectivities etc.). In this thesis we demonstrate a novel approach to dynamical understanding of the cosmic web features -- fundamentally based on the ZA, and it's direct consequence of multistreaming phenomenon.

However, it has to be noted and stressed that almost all the results here pertain to dark matter structures, not baryonic matter distribution of galaxies, stars or gas. While clustering of galaxies is positively correlated with dark matter concentrations, the difference in their dynamics of DM and baryonic gas vast. Perhaps the most important difference in the context of this thesis is the difference of collisional cross-sections. Dark matter particles are collisionless in N-body simulations, hence display multiple velocity streams. The motion of cold baryonic gas resembles that of dark matter only until the first orbit crossing arises. However, streams of gas cannot penetrate through one another, causing layers of neighboring gas layers to collide and result in shock waves. On galactic scales, the gas dynamics is further complicated by processes like radiative cooling and heating, supernova feedback, star formation and more.

@@

This thesis is a comprehensive collection of various cosmic structure analyses in the context of Lagrangian sub-manifold -- from topological studies of voids, to environmental investigation of dark matter haloes. In Chapter \ref{chapter2}, we give a brief overview of topics related to rest of the thesis -- including the Zel'dovich approximation. Lagrangian sub-manifold and multistream fields. Chapter \ref{chapter3} approaches to quantify thresholds based on multistreams with the cosmic web structures. The next two chapters deal with deeper understanding of topological and geometrical features detected in multistream field (in Chapter \ref{chapter4}) and a new approach of detecting dark matter haloes that is independent of heuristic parameters (in Chapter \ref{chapter5}). Comparison of a variety of current cosmic structure finding algorithms are compared with our multistream-based methodology in Chapter \ref{chapter3b}. The concluding Chapter \ref{chapter6} highlights future avenue of similar studies on the Lagrangian sub-manifold -- including detection of caustic surfaces and halo substructure analysis using flip-flop fields.

### 2018-06-15 Draft/Chapter2/background.tex
bruce

ZA is an elegant analytical approximation to describe the non-linear gravitational evolution of collisionless particles in continuous media. Technically it is the first oder Lagrangian perturbation theory, however Zel'dovich suggested to extrapolate it to the beginning of the non-perturbative nonlinear stage and predicted the formation of caustics which are the boundaries of
the first very thin multistream regions dubbed by him  'pancakes'.
ZA describes a dynamical mapping from the initial Lagrangian coordinates $\mathbf{q}$ to Eulerian positions at time $t$. In co-moving coordinates, $\mathbf{x} = \mathbf{r}/a(t)$ (where $\mathbf{r}$ is the physical coordinate  and $a(t)$ is the scale factor; assuming normalization $a(z=0)=1, \mathbf{r}$ are 
the physical coordinates of particles at present ), ZA takes the form:

@@

where the Jacobian $J \left[ \frac{\partial\mathbf{x}}{\partial\mathbf{q}} \right]$ is calculated using Equation \ref{eq:ZA1}. Moreover, diagonalization of the resulting real, symmetric deformation tensor $d_{ij} = - \nabla_q \mathbf{s(q)} =  \partial^2 \psi(\mathbf{q})/ \partial q_i \partial q_j$ in terms of its eigenvalues $\lambda_1(\mathbf{q})$, $\lambda_2(\mathbf{q})$, $\lambda_3(\mathbf{q})$ gives the contraction or expansion along the three principal axes. This reduces the mass density to a convenient form:

@@

Since the deformation tensor $d_{ij}$ and its eigenvalues depend only on the initial density field, the ordered eigenvalues defined in Lagrangian space $\lambda_1(\mathbf{q}) \geq \lambda_2(\mathbf{q}) \geq \lambda_3(\mathbf{q})$ determine collapse condition for masses in Eulerian space (see \cite{Doroshkevich1970} and \cite{Lee1998} {for the PDFs  of the eigen values as well as several other parameters} in the case of Gaussian random fields). In the context of this paper, formation of caustics is of much interest: with increasing $D(t)$, the mass density rises until reaching singularity at $D(t) = 1/\lambda_3(\mathbf{q})$. In Lagrangian space, the caustics stem from these points and their counterparts  in Eulerian space were proposed by Zel'dovich as the 'birthplaces' of the first collapsed structure by gravitational clustering. Now the regions bounded by the caustic surfaces are referred to as {\it Zel'dovich pancakes}. The collapse along other principal axes correspond to formation of filaments and knots \citep{Arnold1982}, Shandarin and Klypin (1984). However simultaneous collapses along all three eigen axes never happen in the case of generic flows.

@@

Furthermore, the analytical understanding of these structures are thoroughly complicated: In a 2-dimensional ZA, for example, there are only two types of fundamental singularities that exist at generic instants of time($A_2$, which are lines and $A_3$, which are the cusp points of $A_2$ lines).   In addition there are two singular points ($A_4$, and $D_4$) that exist  only at particular instants of time: at $A_4$ two cusp $A_3$-points are formed and a smooth part of an $A_2$ line is  transformed in self-crossing
line. In addition there are several transient forms that exist only 
at particular times.
Each of these correspond of formation, mergers, branching and other dynamical processes involving pancakes. \cite{Arnold1982} and \cite{Hidding2014} studied of singularities in 2-dimensional collapse) in exhaustive detail, but similar analytical characterization of 3-dimensional ZA has not been satisfactorily done yet.

@@

\begin{figure}
\begin{minipage}[t]{.99\linewidth}
  \centering\includegraphics[width=8.cm]{Chapter4/Source_v2/fig13.pdf} 
\end{minipage}\hfill
\caption{ Multi-streaming in one-dimension gravitational collapse. Top panel: $(\bf{p}, \bf{x})$ phase-space representation redshift $z_{ini}$ and $z = 0$. Dots represent the dark matter particles. Initially the mass particles are in the linear stage of evolution. At $z = 0$, multiple values of $\bf{p}(\bf{x})$ is seen in the collapsed regions. Middle panel: Equivalent Lagrangian sub-manifold $\bf{q}(\bf{x})$. At $z_{ini}$, the dashed line represents $\bf{q} = \bf{x}$. Number of streams are parametrized from this sub-manifold. Bottom panel: The multistream field $n_{str}$ and the number-density using CIC algorithm, $n_{CIC}$ at $z = 0$. }
\label{fig:phase1d}
\end{figure}

@@

\begin{figure} 
\centering\includegraphics[width=16cm]{Chapter4/Source_v2/fig1.pdf} 
\caption{Three dimensional rendering of the multistream field: the cosmic web structure of a $ 50 h^{-1} \text{Mpc} \times 50 h^{-1} \text{Mpc} \times 50 h^{-1} \text{Mpc}$ slice in a simulation box of side length $100 h^{-1}$ Mpc and $128^3$ particles. The multistream field is calculated at 8 times the native resolution. void(black) is a percolating structure with $n_{str} = 1$. Regions $n_{str} \geq 17$ show a filamentary structure (gray) and the bright spots at the intersections of the filaments are regions with $n_{str} \geq 100$. }
\label{fig:full_3d}
\end{figure}

In three-dimensional simulations, the Lagrangian sub-manifold twists in complicated ways in a six-dimensional phase space. This is due to complexities involving caustic formations in higher dimensions, which is true even in the ZA, see \citealt{Arnold1982} and \citealt{Hidding2014} for detailed analyses of caustic formation. The resulting intricate geometrical structures can be characterized by the $n_{str}$ field. Nearly  $90\%$ of the volume in N-body simulations are single-streamed voids at $z=0$ (\citealt{Shandarin2012}, also see \citealt{Falck2015} for a percolation analysis of single-streaming voids). From the visualizations in \cite{Ramachandra2015} and percolation analysis of \cite{Ramachandra2017}, we also know that the $n_{str} = 3$ regions mostly form connected wall-like structures (also see \autoref{fig:full_3d}), unlike the isolated patches as seen in one-dimensional simulations of \autoref{fig:1d}. The structures become predominantly filamentary at higher thresholds of $ n_{str} \gtrsim 17$. Subsequently, the regions around the multistream maxima have isolated closed surfaces (for example, in \autoref{fig:full}), which may be identified as halo locations.

\begin{figure} 
\centering\includegraphics[width=11cm]{Chapter5/Source_v2/fig2.pdf} 
\caption{Multistream field contours: The multistream field is calculated at 8 times the native resolution. Each inner convex blobs (red) surround local multistream maxima inside. Surrounding outer shell(blue) is not convex throughout the surface, and the outermost gray multistream surface displays a filamentary geometry.}
\label{fig:full}
\end{figure}

Caustic formations and mass accretion are also seen to occur more along the higher streams, which makes the haloes non-spherical, with the alignment generally determined by a complicated interplay  of the intensities of the streams from neighboring filamentary structures. Number of streams corresponding to the dark matter halo also has a local environment dependence. The three small haloes in \autoref{fig:full}, where the number of streams are higher than the neighboring filaments, are aligned along three intersecting filaments. Halo environment studied in \cite{Ramachandra2015} show similar hierarchical variation in $n_{str}$ values. The halo environments are thus very complicated, and empirical thresholds (on multistream or density fields) may not account for all the haloes uniformly. Hence we use a local geometrical method to identify potential haloes in multistream fields.

>>>>

The Zel'dovich Approximation is an elegant analytical approximation to describe the non-linear gravitational evolution of collisionless particles in continuous media. Technically it is the first oder Lagrangian perturbation theory, however Zel'dovich suggested to extrapolate it to the beginning of the non-perturbative nonlinear stage and predicted the formation of caustics which are the boundaries of
the first very thin multistream regions dubbed by him  'pancakes'. The
ZA describes a dynamical mapping from the initial Lagrangian coordinates $\mathbf{q}$ to Eulerian positions at time $t$. In co-moving coordinates, $\mathbf{x} = \mathbf{r}/a(t)$ (where $\mathbf{r}$ is the physical coordinate  and $a(t)$ is the scale factor; assuming normalization $a(z=0)=1, \mathbf{r}$ are 
the physical coordinates of particles at present ), the ZA takes the form:

@@

where the Jacobian $J \left[ \frac{\partial\mathbf{x}}{\partial\mathbf{q}} \right]$ is calculated using Equation \ref{eq:ZA1}. Moreover, diagonalization of the resulting real, symmetric deformation tensor $d_{ij} = - \nabla_q \mathbf{s(q)} =  \partial^2 \psi(\mathbf{q})/ \partial q_i \partial q_j$ in terms of its eigenvalues $\lambda_1(\mathbf{q})$, $\lambda_2(\mathbf{q})$, $\lambda_3(\mathbf{q})$ gives the contraction or expansion along the three principal axes. This reduces the mass density to a convenient form in Lagrangian coordinates:

@@

However, transforming it in Eulerian coordinates requires solving Equation \ref{eq:ZA1} for $\mathbf{q}$, which is not possible analytically in the case of random initial condition. Since the deformation tensor $d_{ij}$ and its eigenvalues depend only on the initial density field, the ordered eigenvalues defined in Lagrangian space $\lambda_1(\mathbf{q}) \geq \lambda_2(\mathbf{q}) \geq \lambda_3(\mathbf{q})$ determine collapse condition for masses in Eulerian space (see \cite{Doroshkevich1970} and \cite{Lee1998} {for the PDFs  of the eigen values as well as several other parameters} in the case of Gaussian random fields). In the context of this paper, formation of caustics is of much interest: with increasing $D(t)$, the mass density rises until reaching singularity at $D_{1}(t) = 1/\lambda_1(\mathbf{q})$. In Lagrangian space, the caustics stem from these points and their counterparts  in Eulerian space were proposed by Zel'dovich as the `birthplaces' of the first collapsed structure by gravitational clustering. The collapse along other principal axes correspond to formation of filaments and knots \citep{Arnold1982}, Shandarin and Klypin (1984). However simultaneous collapses along all three eigen axes never happen in the case of generic flows.

@@

Furthermore, the analytical understanding of these structures are thoroughly complicated: In a 2-dimensional ZA scenario, for example, there are only two types of fundamental singularities that exist at generic instants of time ($A_2$, which are lines and $A_3$, which are the cusp points of $A_2$ lines).   In addition there are two singular points ($A_4$, and $D_4$) that exist  only at particular instants of time: at $A_4$ two cusp $A_3$-points are formed and a smooth part of an $A_2$ line is  transformed in self-crossing
line. In addition there are several transient forms that exist only 
at particular times.
Each of these correspond of formation, mergers, branching and other dynamical processes involving pancakes. \cite{Arnold1982} and \cite{Hidding2014} studied of singularities in 2-dimensional collapse) in exhaustive detail, but similar analytical characterization of 3-dimensional Zel'dovich approximation has not been satisfactorily done yet.

@@

\begin{figure}
\begin{minipage}[t]{.99\linewidth}
  \centering\includegraphics[width=8.cm]{Chapter4/Source_v2/fig13.pdf} 
\end{minipage}\hfill
\caption{ Multi-streaming in one-dimension gravitational collapse. Top panel: $(\bf{p}, \bf{x})$ phase-space representation redshift $z_{ini}$ and $z = 0$. Dots represent the dark matter particles. Initially the mass particles are in the linear stage of evolution. At $z = 0$, multiple values of $\bf{p}(\bf{x})$ is seen in the collapsed regions. Middle panel: Equivalent Lagrangian sub-manifold $\bf{q}(\bf{x})$. Blue line represents the sub-manifold at $z_{ini}$. Number of streams are parametrized from this sub-manifold. Bottom panel: The multistream field $n_{str}$ and the number-density using CIC algorithm, $n_{CIC}$ at $z = 0$. }
\label{fig:phase1d}
\end{figure}

@@

\begin{figure} 
\centering\includegraphics[width=16cm]{Chapter4/Source_v2/fig1.pdf} 
\caption{Three dimensional rendering of the multistream field: the cosmic web structure of a $ 50 h^{-1} \text{Mpc} \times 50 h^{-1} \text{Mpc} \times 50 h^{-1} \text{Mpc}$ slice in a simulation box of side length $100 h^{-1}$ Mpc and $128^3$ particles. The multistream field is calculated at 8 times the native resolution. Void (black) is a percolating structure with $n_{str} = 1$. Regions $n_{str} \geq 17$ show a filamentary structure (gray) and the bright spots at the intersections of the filaments are regions with $n_{str} \geq 100$. }
\label{fig:full_3d}
\end{figure}

In three-dimensional simulations, the Lagrangian sub-manifold twists in complicated ways in a six-dimensional phase space. This is due to complexities involving caustic formations in higher dimensions, which is true even in the ZA, see \citealt{Arnold1982} and \citealt{Hidding2014} for detailed analyses of caustic formation. The resulting intricate geometrical structures can be characterized by the $n_{str}$ field. Nearly  $90\%$ of the volume in N-body simulations are single-streamed voids at $z=0$ (\citealt{Shandarin2012}, also see \citealt{Falck2015} for a percolation analysis of single-streaming voids). From the visualizations in \cite{Ramachandra2015} and percolation analysis of \cite{Ramachandra2017}, we also know that the $n_{str} = 3$ regions mostly form connected wall-like structures, unlike the isolated patches as seen in one-dimensional simulations of \autoref{fig:1d}. The structures become predominantly filamentary at higher thresholds of $ n_{str} \gtrsim 17$ (also see \autoref{fig:full_3d}). Subsequently, the regions around the multistream maxima have isolated closed surfaces (for example, in \autoref{fig:3full}), which may be identified as halo locations.

\begin{figure} 
\centering\includegraphics[width=11cm]{Chapter5/Source_v2/fig2.pdf} 
\caption{Multistream field contours: The multistream field is calculated at 8 times the native resolution. Each inner convex blobs (red) surround local multistream maxima inside. Surrounding outer shell (blue) is not convex throughout the surface, and the outermost gray multistream surface displays the transition to filamentary geometry.}
\label{fig:3full}
\end{figure}

Caustic formations and mass accretion are also seen to occur more along the higher streams, which makes the haloes non-spherical, with the alignment generally determined by a complicated interplay  of the intensities of the streams from neighboring filamentary structures. Number of streams corresponding to the dark matter halo also has a local environment dependence. The three small haloes in \autoref{fig:3full}, where the number of streams are higher than the neighboring filaments, are aligned along three intersecting filaments. Halo environment studied in \cite{Ramachandra2015} show similar hierarchical variation in $n_{str}$ values. The halo environments are thus very complicated, and empirical thresholds (on multistream or density fields) may not account for all the haloes uniformly. Hence we use a local geometrical method to identify potential haloes in multistream fields in \cite{Ramachandra2017b}
